Data preparation

### 2023-03-29 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Fixing errors, checking data after addressing problems

```{r}
prep_xx <- 
  prep_building %>% 
  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
  distinct() %>% 
  mutate(
    position_category_imputed = case_when(is.na(position_category_code) ~ 1,
                                          is.na(position_category_description) ~ 1,
                                          TRUE ~ 0) 
  ) %>% 
  arrange(person_id, date) %>% 
  group_by(person_id) %>% 
  fill(position_category_code, .direction = "downup") %>% 
  fill(position_category_description, .direction = "downup") %>% 
  ungroup() %>% 
  mutate(
    across(
      .cols = all_of(problem_variable %>% pull(variable)),
      .fns = ~case_when(is.na(.) ~ "(Missing)",
                        TRUE ~ .)
    )
  )
  )

@@

```{r}
prep_xx %>% 
  filter(supervisor_e_mail_address.y == supervisor_e_mail_address.z) %>% 
  count(supervisor_display_name)
  arrange(desc(supervisor_e_mail_address.z))
```

@@

>>>>

```{r}
prep_xx <- 
  prep_building %>% 
  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
  distinct() %>% 
  mutate(
    position_category_imputed = case_when(is.na(position_category_code) ~ 1,
                                          is.na(position_category_description) ~ 1,
                                          TRUE ~ 0) 
  ) %>% 
  arrange(person_id, date) %>% 
  group_by(person_id) %>% 
  fill(position_category_code, .direction = "downup") %>% 
  fill(position_category_description, .direction = "downup") %>% 
  ungroup() %>% 
  mutate(
    across(
      .cols = all_of(problem_variable %>% pull(variable)),
      .fns = ~case_when(is.na(.) ~ "(Missing)",
                        TRUE ~ .)
    )
  )

@@

```{r}
prep_xx %>% 
  filter(supervisor_e_mail_address.y == supervisor_e_mail_address.z) %>% 
  count(supervisor_display_name)
```

@@

problem_groups
```
